Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-06-25 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
adding description of varying fit interval figure

		Faint, high-temperature emission in active region cores has long been predicted as a signature of nanoflare heating. However, the detection of such emission has proved difficult due to a combination of the efficiency of thermal conduction, non-equilibrium ionization, and inadequate instrument sensitivity. In this second paper in our series on ``hot'' non-flaring plasma in active regions, we investigate the influence of repeating nanoflares of varying frequency on the resulting emission measure di . We have used an efficient two-fluid hydrodynamic model to carry out a parameter exploration in preferentially heated species, heating event frequency, and the power-law index determining the distribution of event energies. By computing the emission measure distributions and calculating their ``hotward'' slopes, we have concluded that not treating the electron and ion populations separately leads to a mischaracterization of the hot emission. Additionally, we find that, while emission due to separate electron and ion heating differs greatly hotward of the peak, the respective coolward emission measure slopes are similar such that a distinction between the heating of one species over another based on this criteria alone is not possible. 

@@

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim3.6\times10^{-3}$. \hl{In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.} Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by 

@@

		\caption{Total Parameter space covered. ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions. \hl{Are we going to look at the single-fluid case? If not, remove if here and reconsider total number of heating functions.}}

@@

	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to compute the non-equilibrium ionization states and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium. Using $T_eff$, we are then able to compute a corresponding NEI emission measure distribution.

@@

		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). The solid lines in the power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates one standard deviation from the mean. The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}

@@

	\par Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although $\mathrm{EM}(T)$ for all three types of heating functions widen with increasing wait time, their dependence on $t_N$ is quite different. The uniform (red) and power-law (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the power-law, $\beta=1$ curve (green) extends to cooler temperatures much more rapidly. For example, at $t_N=1500$ s, both the uniform and power-law cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK. Contrastingly, on the hot side, the power-law and $\beta=1$ curves evolve nearly identically with increasing $t_N$ while the unfiorm heating case shows a cutoff at much lower temperatures, particularly for $t_N\le2500$ s. 

@@

		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for an intermediate heating frequency, $t_N=2500$ s for uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}

@@

	\par \autoref{fig:single_em} shows the same results as \autoref{fig:el_em} and \autoref{fig:ion_em}, but for the single-fluid case in which electron-ion equilibrium is assumed at all times. To compute these $\mathrm{EM}$ curves, we have used the original, single-fluid EBTEL model as described in \citet{klimchuk_highly_2008} and \citet{cargill_enthalpy-based_2012}. The equivalent parameter space that was investigated with the modified two-fluid EBTEL model is explored with the single-fluid EBTEL code as well.

@@

	\par We compute the hot and cool emission measure slopes in the same manner as the electron and ion heating cases. We first note that the cool emission measure slopes are comparable to those in both the electron and ion heating cases. In particular, we find $2\lesssim a\lesssim5$ for all values of $t_N$ as expected. Again, we confirm the validity of our linear fit to the cool emission by computing the derivative $d\log{\mathrm{EM}}/d\log{T}$ in the lower right panel of \autoref{fig:single_em}. For $T_N\gtrsim2000$ s, the slope is bounded between 2 and 3 on the interval $6.0\le\log{T}\le6.6$. 

@@

	\par The hot emission measure in the single-fluid case differs significantly from the two-fluid case. In contrast to the electron heating case in \autoref{fig:el_em}, the $\mathrm{EM}$ curves in the left panel of \autoref{fig:single_em} show no hot shoulder. This is further confirmed by the lower right panel; the derivative, in contrast to the electron heating case, shows no peak near $10^7$ K. For low $t_N$, $d\log{\mathrm{EM}}/d\log{T}$ is monotonically decreasing for $\log{T}\gtrsim6.6$. For $T_N\ge3000$ s, $d\log{\mathrm{EM}}/d\log{T}$ is relatively flat for $\log{T}\ge7.0$, indicating that a power-law provides a good description of the hot emission in this region. This is confirmed by noting the agreement between the fit lines and the $\mathrm{EM}$ curves in the left panel.
	\par Comparing the top right panels of \autoref{fig:single_em} and \autoref{fig:el_em} further highlights the enhanced hot emission in the electron case. For high $t_N$, the hot emission slopes in the electron case converge to a value just above 3; for the single-fluid case, the hot slopes converge to approximately 4.5. Thus, while a single power-law is not a good descriptor for the hot emission in the case of electron heating, the slope still captures the enhanced hot shoulder relative to the weaker hot emission of the single-fluid case. Additionally, comparing the single-fluid case to the ion heating case in \autoref{fig:ion_em}, it is obvious that the single-fluid case shows a great deal more hot emission as the $\mathrm{EM}$ curves in the left panel of \autoref{fig:single_em} extend well above $10^7$ K while those in the left panel of \autoref{fig:ion_em} show a steep cutoff at temperatures just above the peak.

@@

	%\par To characterize the emission measure, we compute the slopes on both the cool and hot sides of the peak. To be consistent with past observational and computational studies of cool emission \citep[see][and references therein]{bradshaw_diagnosing_2012}, we fit the cool slope on the interval $6.0\le\log{T}\le6.6$. Contrastingly, past studies of hot emission are less abundant; thus, the ``hot'' region where the $\mathrm{EM}$ is thought to follow a power-law is far less constrained. In order to best describe the steepness of the emission measure hotward of the peak, we choose to fit $\mathrm{EM}$ between the temperatures at which the emission measure is $99\%$ and $92\%$ of the peak value. We have no physical reason for choosing these particular bounds, but note that on this interval, the mean hotward emission is reasonably well-described by a power-law relationship. Fitting too close to the wide peak leads to misleadingly shallow slopes while fitting too close to the steep drop near $\log{T}\sim7.5$ results in steep slopes not particularly representative of the hotward emission. We perform the fit using the Levenberg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}.
	\par We first briefly consider the calculated cool emission measure slopes. Looking at the top right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we note that in the cases of electron and ion heating, the cool emission measure slopes are consistent with both observational and modeling studies of cool emission in AR cores, having values that fall within the range $2\le a\le5$ \citep[and references therein]{bradshaw_diagnosing_2012}. Furthermore, the cool slopes computed using our new modified EBTEL model, with a heating function of the form $Q\propto T_N^{\beta}$, are consistent with those values reported in \citet{cargill_active_2014} and show a dependence on the waiting time $t_N$.  
	\par Additionally, looking at the bottom right panels of \autoref{fig:el_em} and \autoref{fig:ion_em}, we see that, within the range $6.0\le\log{T}\le6.6$, the $\mathrm{EM}$ is reasonably well-described by a power-law, where $2\lesssim d\log{\mathrm{EM}/d\log{T}}\lesssim3$. Comparing the cases of electron and ion heating for both the cool slopes and $d\log{\mathrm{EM}/d\log{T}}$ on $6.0\le\log{T}\le6.6$, there are no substantial differences for all values of $t_N$ considered.
	\par This is not the case for the hot emission measure. Looking first at the case of electron heating in \autoref{fig:el_em}, we note that there is a pronounced ``hot shoulder'' in the emission measure (left panel) just above $10^7$ K for $T_N\gtrsim2000$ s. This feature is even more evident when looking at the derivative of $\mathrm{EM}$ in the bottom right panel of \autoref{fig:el_em}. The peak between $10^7$ and $10^{7.5}$ K shows how the $\mathrm{EM}$ flattens out around $10^7$ K, indicating an enhanced hot emission measure. Considering the large range of values of $d\log{\mathrm{EM}}/d\log{T}$ on the interval over which the fit was performed, we acknowledge that a single power-law fit is not a good description of the hot emission measure in the case of electron heating.
	\par Contrastingly, we have not calculated the hot emission measure slopes for the case of ion heating. Looking at the left panel of \autoref{fig:ion_em}, for $T_N\gtrsim1000$ s, the $\mathrm{EM}$ peak is wide with a sharp cutoff just above $10^7$ K. There is no substantial emission measure component above $10^7$ K and, consequently, no hot shoulder as in the electron heating case. Applying the fitting procedure outlined above to the hot emission in the case of ion heating yields meaningful results for only a few short $t_N$. Thus, as in the case of electron heating, the resulting hot emission measure from ion heating is also not well described by a power-law. The lower right panel of \autoref{fig:ion_em} further highlights this by showing that around $10^7$ K, $d\log{\mathrm{EM}}/d\log{T}\to-\infty$.

@@

		\caption{\textbf{Left:} EM slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $EM(T)$. \textbf{Right:} Emission measure distribution with overlaid hot and cool fit lines for varying fit intervals.}

@@

		\caption{Electron heating emission measure ratio for an EIS/MaGIXS line pair}

@@

	\par As mentioned in \autoref{sec:intro}, NEI can make it difficult to observe emission signatures from nanoflare-heated plasma because the heating timescale is shorter than the ionization timescale such that the charge state of the plasma is not representative of the plasma temperature. In order to diagnose how NEI might affect hot emission measure slopes, we use $n$ and $T_e$ profiles from our modified EBTEL code along with the method outlined by \citet{bradshaw_numerical_2009} to compute $T_{eff}$, the temperature that would be measured based on the actual ionization states. An effective emission measure distribution, $\mathrm{EM}_{eff}$, can then be calculated. Following \citetalias{barnes_inference_2016}, we use iron (Fe) and the ionization states Fe IX through FeXXV.

@@

	\par As the calculation of $T_{eff}$ is significantly more expensive than an EBTEL calculation, we do not compute $\mathrm{EM}_{eff}$ for the entire parameter space and instead consider only a small number of single-pulse test cases of duration $\tau_H=100$ s and peak heating rate $H_0=0.8$ erg cm$^{-3}$ s$^{-1}$. \autoref{fig:teff_test_case} shows temperature and density profiles (left column)  and emission measure distributions (right column) for the cases where NEI is (dashed) and is not (solid) included. These profiles are computed for all preferentially-heated species (electron, ion, single-fluid). For all three species, we note that including NEI in the calculation of the cool slope makes essentially no difference .

@@

	\par As in \autoref{fig:ion_em}, we do not compute the hot slope for the case of ion heating. Looking at the right panel in the middle row of \autoref{fig:teff_test_case}, we see that the inclusion of NEI in the case of ion heating has little to no effect on the emission measure. This is confirmed by the left panel of the middle row which shows that the difference between $T$ and $T_{eff}$ is relatively small and only occurs at low densities. Conversely, in the single-fluid and electron-heating cases, $T$ and $T_{eff}$ differ greatly during the heating phase and NEI has two distinct effects on the $\mathrm{EM}$: it leads to an overestimation of the amount of emission in the mid-range hot temperatures ($7.0\lesssim\log{T}\lesssim7.2$) and causes a steeper cutoff in the emission at lower temperatures (before $\log{T}\approx7.25$) compared to the case where NEI is not included. Interestingly, in both the electron-heating (first row) and single-fluid (third row) cases, $b_{eff}<b$ though we note that in the electron-heating case (first row), a power-law fit does not adequately describe the hot side of the $\mathrm{EM}$ distribution.
	\par To compare the effects of varying $\alpha$, $\beta$, and $t_N$ for each species (i.e. electron, ion, single-fluid), we construct histograms of hot and cool emission measure slopes for each parameter space point. Recall that in the case where the distributions of heating event energies are non-uniform, we have $N_{R}$ emission measure slopes to properly account for the statistical spread in hot emission measure slopes due to power-law distributions.

@@

	\par Concerning the distributions of cool slopes grouped by type of heating function (bottom row of \autoref{fig:histos}), we note that there are no discernible differences between the cases of electron and ion heating. In both cases, all heating functions except for those where $\beta=1$ are peaked sharply between 2 and 2.5. In the case where $\beta=1$ (for all $\alpha$), the distribution is peaked between 2.5 and 3, with the width of the distribution increasing as $\alpha$ steepens. This larger range of cool emission measure slopes for the case of $\beta=1$ is consistent with \citet{cargill_active_2014}.
	\par As stated in \autoref{subsec:electron_ion_heating}, we choose not to show the hot emission measure slopes for the ion heating case as they are not representative of the emission measure distribution hotward of the peak as evidenced by the left and bottom right panels of \autoref{fig:ion_em}. Instead, we compare the hot emission measure slopes of the electron heating and single-fluid cases, the bottom left and bottom right panels of \autoref{fig:histos}, respectively. In both cases, for $T_N<3000$ s, we see a strong dependence on $t_N$ while for $T_N\ge3000$ s, the slopes tend to be sharply peaked around a single value. In the electron heating case, distributions for $T_N<3000$ s tend to be more narrow than their single-fluid counterparts and centered at lower values (i.e. more shallow hot slopes). Most notably, for $T_N\ge4000$ s, the electron heating hot emission measure slopes are peaked between 3 and 3.5 while the single-fluid slopes are peaked at $\sim4.5$. 

@@

	\par However, looking at the left panels in the first and third rows of \autoref{fig:teff_test_case}, we see that just after the heating ends at 100 s, $T_{eff}>T$ due to the fact that the thermal conduction timescale is shorter than the ionization equilibration timescale. This lag in the charge state due to the efficiency of thermal conduction leads to the mid-range hot temperature emission enhancement seen in the right panels of the first and third rows of \autoref{fig:teff_test_case}. 

@@

	\hl{Acknowledge some things here.} 

>>>>

		Faint, high-temperature emission in active region cores has long been predicted as a signature of nanoflare heating. However, the detection of such emission has proved difficult due to a combination of the efficiency of thermal conduction, non-equilibrium ionization, and inadequate instrument sensitivity. In this second paper in our series on ``hot'' non-flaring plasma in active regions, we investigate the influence of repeating nanoflares of varying frequency on the resulting emission measure distribution . We have used an efficient two-fluid hydrodynamic model to carry out a parameter exploration in preferentially heated species, heating event frequency, and the power-law index determining the distribution of event energies. We compute the emission measure distribution for each point in our multi-dimensional heating parameter space in an effort to understand how each of these variables impacts the observed emission. Additionally, we calculate several observables and compare their efficacy in capturing the character of both the hot and cool parts of the emission measure distribution. 

@@

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim3.6\times10^{-3}$. In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored. Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by 

@@

		\caption{Total Parameter space covered. ``single'' indicates a single-fluid model. $\alpha$ is the power-law index and $\beta$ indicates the scaling in the relationship $Q\propto T_N^{\beta}$, where $\beta=0$ corresponds to the case where $t_N$ and the event energy are independent. Note that $(3~\alpha~\mathrm{values})\times(2~\beta~\mathrm{values})+\mathrm{uniform~heating}=$ 7 different types of heating functions.}

@@

	\par As in \citetalias{barnes_inference_2016}, we use the numerical code\footnote{This code has been made freely available by the author and can be downloaded at: \url{https://github.com/rice-solar-physics/IonPopSolver}.} outlined in \citet{bradshaw_numerical_2009} to asses the impact of NEI on our results. Given a temperature ($T(t)$) and density ($n(t)$) profile from EBTEL, we compute the non-equilibrium ionization states for Fe IX through XXVII and the corresponding effective electron temperature, $T_{eff}$ that would be inferred by assuming ionization equilibrium. Using $T_{eff}$, we are then able to compute a corresponding NEI emission measure distribution.

@@

		\caption{Emission measure distributions for waiting-times $t_N=250,750,1500,2500,3750,5000$ s in the single-fluid case. The three types of heating functions shown are uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green). The solid lines in the power-law cases show the mean $\mathrm{EM}(T)$ over $N_R$ runs and the shading indicates $1\sigma$ from the mean. The dashed lines denote the corresponding $\mathrm{EM}(T_{eff})$ distribution.}

@@

	\par Looking at the different curves in each panel of \autoref{fig:single_em}, it is important to note that, although $\mathrm{EM}(T)$ for all three types of heating functions widen with increasing wait time, their dependence on $t_N$ is quite different. The uniform (red) and power-law (blue) $\mathrm{EM}(T)$ curves evolve similarly as they extend to cooler temperatures with increasing $t_N$ while the power-law, $\beta=1$ curve (green) extends to cooler temperatures much more rapidly. For example, at $t_N=1500$ s, both the uniform and power-law cases show little to no emission below 2 MK while the $\beta=1$ cases extends to temperatures well below 1 MK \citep{cargill_active_2014}. Contrastingly, on the hot side, the power-law and $\beta=1$ curves evolve nearly identically with increasing $t_N$ while the unfiorm heating case shows a cutoff at much lower temperatures, particularly for $t_N\le2500$ s. 

@@

		\caption{Example heating (top), temperature (middle), and density (bottom) profiles for the case in which only the electrons are heated and an intermediate heating frequency of $t_N=2500$ s. The three curves shown in each panel correspond to uniform heating rates (red), heating rates chosen from a power-law distribution of $\alpha=-2.5$ (blue), and heating rates chosen from a power-law distribution of $\alpha=-2.5$ where the time between successive events is proportional to the heating rate of the preceding event (green).}
		\label{fig:nT_sample_profiles}

@@

	\par In the single-fluid and electron heating cases, while $\mathrm{EM}(T)$ in the uniform and power-law heating cases generally agree for low-frequency heating ($t_N=5000$ s), for intermediate frequencies ($t_N\approx750-2500$ s), the power-law cases show an enhanced high-temperature component compared to the uniform case as seen in \autoref{fig:single_em} and \autoref{fig:el_em}.

@@

	\par\autoref{fig:nT_sample_profiles} shows sample heating, temperature, and density profiles for an intermediate heating frequency ($t_N=2500$ s), in the case where only the electrons are heated, for the three different types of heating functions. In the uniform heating rate case (red), each event has a max heating rate of $H_0$ such that the loop undergoes $N\approx30$ identical heating and cooling cycles, each time reaching a maximum temperature and density of $T_{max,0}$ and $n_{max,0}$, respectively. Recall from \autoref{eq:heating_rate_constraint} that the total energy injected into the loop is constrained such that $H_0=(1/N)\sum_{i=1}^NH_i$. In the case where the heating rates are distributed according to a power-law, there will be many events where $H_i<H_0$ and a few events where $H_i\gg H_0$. 

@@

	\par The effect of these few higher energy events can be seen where the peak temperature of event $i$ is greater than $T_{max,0}$ in the two power-law cases (blue and green curves) in the middle panel of \autoref{fig:nT_sample_profiles} 

@@

	\par\hl{Discuss usefullness of hot slope versus cool slope via figure; discuss advantages of em ratio; discuss em ratio figures; break into subsections?}

@@

		\caption{Power-law fits to a sample emission measure distribution constructed from a loop plasma in which only the electrons were heated by events chosen from a power-law distribution with $\alpha=-2.5$ and equally spaced by an interval of $t_N=5000$ s. \textbf{Left:} $\mathrm{EM}(T)$ slope as a function of upper bound on fit interval for both the hot (red) and cool (blue) side of $\mathrm{EM}(T)$. The shading denotes the uncertainty of the fit. The bottom axis corresponds to the varying upper limit on the fit to the cool side while the top axis corresponds to the varying upper limit on the fit to the hot side. \textbf{Right:} $\mathrm{EM}(T)$ with the overlaid hot (red) and cool (blue) fit lines whose slopes correspond to those shown on the left. The cool power-law fits describe describe $\mathrm{EM}(T)$ for $T<4$ MK quite well while a similar fit on the hot side fails to accurately describe the shape of the emission measure distribution for $T>4$ MK.}
		\label{fig:em_slope_varying_bounds}

@@

		\caption{Electron heating emission measure ratio for an EIS/MaGIXS line pair.\hl{Need a more descriptive caption here!}}

@@

@@

	\par We now examine several observables often used to characterize the emission measure distribution. The most common observable is the emission measure slope $a$ such that $\mathrm{EM}\propto T^a$ for $10^{5.5}\le T\le10^{6.6}$ K. Both observational and modeling studies have found that $2<a<5$ \citep[see Table 3 of][]{bradshaw_diagnosing_2012} and in particular, \citet{cargill_active_2014} found that a heating function of the form $t_N\propto\varepsilon$ was needed in order to account for this range of slopes. Additionally, a similar scaling of $\mathrm{EM}\propto T^{-b}$ for $10^{6.6}\le T\le10^{7.0}$ has been claimed though measurements of $b$ have been subject to large uncertainties \citep{warren_systematic_2012}.

@@

	\par\autoref{fig:em_slope_varying_bounds} shows an example of how both $T^a$ and $T^{-b}$ can be fit to the cool and hot sides of $\mathrm{EM}(T)$, respectively. We fit $\log{\mathrm{EM}}$ to $a\log{T}$ on $\log{T_{c,min}}<\log{T}<\log{T_{c,max}}$ and $-b\log{T}$ on $\log{T_{h,min}}<\log{T}<\log{T_{h,max}}$ using the Levenburg-Marquardt algorithm for least-squares curve fitting as implemented in the SciPy scientific Python package \citep{van_der_walt_numpy_2011}. We fix the lower limit on each interval such that $T_{c,min}=10^{5.7}$ K and $T_{h,min} = 10^{6.7}$  K and vary the upper limits over $10^{6.1}<T_{c,max}<10^{6.5}$ and $10^{6.8}<T_{h,max}<10^{7.2}$. The left panel of \autoref{fig:em_slope_varying_bounds} shows the $a$ (blue) and $b$ (red) as a function upper limit of the fit interval, $T_{c,max}$ (bottom axis) and $T_{h,max}$ (top axis), respectively. The shading denotes the uncertainty of the fit. The right panel of \autoref{fig:em_slope_varying_bounds} shows the resulting fit lines superimposed on the emission measure distribution.
	%%%%%%%%%

@@

@@

@@

	WTB was provided travel support to the Coronal Loops Workshop VII held in Cambridge, UK, July 21-23, 2015, at which a preliminary version of this work was presented, by NSF award number 1536094. This work was supported in part by the Big-Data Private-Cloud Research Cyberinfrastructure MRI-award funded by NSF under grant CNS-1338099 and by Rice University.
